Probability

### 2016-04-25 prob.tex
prob.tex \section{Quantum Probability Spaces} updated?

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\mu_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$ and extend the domain of the Born rule to mixed
state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$ and extend the domain of the Born rule to mixed
state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
